---
output:
  html_document: 
    code_folding: hide
    df_print: paged
    theme: flatly 
    highlight: tango
    toc: yes
    toc_depth: 2
    number_sections: yes
  pdf_document: default
---


---
title: "Sales Report"
author: "Harry Kalsted"
date: "7/19/2022"
---


```{r setup, include=FALSE}
# The code chunk name is r setup
# We are setting echo = FALSE because this is a sales report. This is being shared with non-technical people.
# We added both message = FALSE and warning = FALSE
# We set out.width and out.height to 100%, which means plots will fill up the entire screen
# fig.pos = "center" will center the images you create
# We set dpi = 300 to make the images seem crisper
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      out.width = "100%",
                      out.height = "100%",
                      fig.pos = "center",
                      dpi = 300)
```


```{r libraries}
# The code chunk name is r libraries
library(tidyverse)
library(lubridate)
library(tidyquant)
library(plotly)

```


```{r scripts}
# The code chunk name is r scripts
# We are importing the plot_total_sales and plot_categories functions we created in a separate project
source("../00_scripts/plot_sales.R")

```


```{r import data}
# The code chunk name is r import data
# Here we are importing the bike_orderlines dataset in rds form
# We have a 15,644 x 13 tibble
bike_orderlines_tbl <- read_rds("../00_data/bike_sales/data_wrangled/bike_orderlines.rds")
```


# Total Sales Charts {.tabset .tabset-fade .tabset-pills}


## Quarterly Sales Trends


```{r quarterly sales}
# The code chunk name is r quarterly sales
# We are plotting the quarterly sales of our data
plot_total_sales(unit = "quarterly")
```


## Monthly Sales Trends


```{r monthly sales, out.height="500px"}
# The code chunk name is r monthly sales
# We adjusted the pixels to 500 to make it look better in the tabbed format
# We are plotting the monthly sales of our data
plot_total_sales(unit = "monthly")
```


## Weekly Sales Trends


```{r weekly sales}
# The code chunk name is r weekly sales
# We are plotting the weekly sales of our data
# The date format will come out as 2014-06-01, etc. 
plot_total_sales(unit = "weekly", date_format = "%Y-%m-%d")
```


# Category Sales Charts {.tabset .tabset-fade}


## Road {.tabset .tabset-fade .tabset-pills}


### Quarterly


```{r road quarterly, out.height="1000px"}
# The code chunk name is r road quarterly
# We are plotting quarterly sales for the bike category "road"
# We adjusted the out.height to 1000px so the 4 charts would look good stacked on top of each other
plot_categories(category_1 = "Road", unit = "quarterly", ncol = 1)
```


### Monthly


```{r road monthly, out.height="1000px"}
# The code chunk name is r road monthly
# We are plotting monthly sales for the bike category "road"
# We adjusted the out.height to 1000px so the 4 charts would look good stacked on top of each other
plot_categories(category_1 = "Road", unit = "monthly", ncol = 1)
```


### Weekly


```{r road weekly, out.height="1000px"}
# The code chunk name is r road weekly
# We are plotting weekly sales for the bike category "road"
# We adjusted the out.height to 1000px so the 4 charts would look good stacked on top of each other
# The date format will be 2013-07-05, etc
plot_categories(category_1 = "Road", unit = "weekly", date_format = "%Y-%m-%d", ncol = 1)
```


## Mountain {.tabset .tabset-fade .tabset-pills}


### Quarterly


```{r mountain quarterly, out.height="1000px"}
# The code chunk name is r mountain quarterly
# We are plotting quarterly sales for the bike category "mountain"
# We adjusted the out.height to 1000px so the 4 charts would look good stacked on top of each other
plot_categories(category_1 = "Mountain", unit = "quarterly", ncol = 1)
```


### Monthly


```{r mountain monthly, out.height="1000px"}
# The code chunk name is r mountain monthly
# We are plotting monthly sales for the bike category "mountain"
# We adjusted the out.height to 1000px so the 4 charts would look good stacked on top of each other
plot_categories(category_1 = "Mountain", unit = "monthly", ncol = 1)
```


### Weekly


```{r mountain weekly, out.height="1000px"}
# The code chunk name is r mountain weekly
# We are plotting weekly sales for the bike category "mountain"
# We adjusted the out.height to 1000px so the 4 charts would look good stacked on top of each other
plot_categories(category_1 = "Mountain", unit = "weekly", date_format = "%Y-%m-%d", ncol = 1)
```





















The first thing we did was click on a new RMarkdown document, gave it a title, and gave it an author

Then we added: code_folding, df_print, theme, highlight, toc, toc_depth, and number_sections to the YAML

When using toc, make sure to start with H1 headers, which are used to generate the toc

ctrl + alt + i will create a code chunk

We added {.tabset .tabset-fade .tabset-pills} to the H1 headers. 