---
title: Harry is Learning R-Markdown
author: "Harry Kalsted"
date: "6/9/2022"
output: html_document
---





The below text is a header

# Basic Analysis of the Cars Dataset

The below text is a sub-header

## By Harry Kalsted

Here is some bolding

**Part One**

Below is a chunk of code to run. The symbol is (`) NOT ('). You must initiate with three (`) and close with three (`)

We are importing the cars dataset into R with data(cars)

We are looking at the structure of the cars dataset with str(cars)

We are looking at a basic summary of the cars dataset with summary(cars)

We are plotting the cars dataset with plot(cars)

```{r}
data(cars)
str(cars)
summary(cars)
plot(cars)
```

Here is some more bolding

**Part Two**

Below is a another chunk of code to run

We are looking at a histogram of the speed column in the cars dataset with hist(cars$speed)

We are looking at a boxplot of the distance column in the cars dataset with boxplot(cars$dist)

```{r}
hist(cars$speed)
boxplot(cars$dist)
```

Below is IN-LINE R code

We are typing "the average speed of cars was": and then a calculation done in R via mean(cars$speed)

The average speed of cars was `r mean(cars$speed)`

Below is another header. We are just denoting the end of the project

# The End