---
title: Harry is Learning R-Markdown
author: "Harry Kalsted"
date: "6/9/2022"
output: 
  html_document: 
    toc: yes
---

You can add a Table of Contents by going to Output Options and clicking on Table of Contents.

The TOC will use the headers you created in your document as a way to structure the TOC.

When you Knit the R-markdown document to HTML, the TOC will appear near the top and you can simply click where you want to go

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 


The below text is a header. One pound sign gives you a main header

# Basic Analysis of the Cars Dataset

The below text is a sub-header. Two pound signs give you a sub-header

## By Harry Kalsted

The below text is Heading Three. Three pound signs lead to that. Increase pound signs up to six for more sub-headers

### For Work

Here is some bolding

**Part One**

Below is a chunk of code to run. The symbol is the SLANTY quote mark. You must initiate and close with three of them.

You must also include {r} after the first three slanty quote marks to initiate a code chunk. 

We are importing the cars dataset into R with data(cars)

We are looking at the first few rows of the dataset with head(cars)

We are looking at the structure of the cars dataset with str(cars)

We are looking at a basic summary of the cars dataset with summary(cars)

We are plotting the cars dataset with plot(cars)

```{r}
#Here we are importing the cars dataset that is already in R
data(cars)

#Here we are looking at the first few rows of the cars dataset
head(cars)

#Here we are looking at the structure of the cars dataset
str(cars)

#Here we are looking at a summary of the cars dataset
summary(cars)

#Here we are looking at a basic plot of the cars dataset
plot(cars)
```

Here is some more bolding

**Part Two**

Below is a another chunk of code to run

We are looking at a histogram of the speed column in the cars dataset with hist(cars$speed)

We are looking at a boxplot of the distance column in the cars dataset with boxplot(cars$dist)

```{r}
#Here is a histogram plotting the speed of the cars
hist(cars$speed)

#Here is a boxplot plotting the distance of the cars
boxplot(cars$dist)
```

Below is IN-LINE R code

We are typing "the average speed of cars was": and then a calculation done in R via mean(cars$speed)

The average speed of cars was `r mean(cars$speed)`


**Part Three - Extra Stuff to Know**


Using one asterisk on each side of a word will italicize it like this *italic*


Using three asterisks on each side of a word will bold-italicize it like this ***bold italic***


You can list items simply by numbering them like below

1. List Item 1

2. List Item 2


You can use a dash or asterisk to create bullet points like below

- Bullet Point 1

- Bullet Point 2


You can add links to your R-markdown document like below. Use brackets to name the link. 

Then use parentheses after with the actual hyperlink. Make sure the https is included

[here is a link to a R-markdown tutorial on Youtube](https://www.youtube.com/watch?v=K418swtFnik)



Below is another header. We are just denoting the end of the project. We are bolding the header.

# **The End**